### 2018-04-27 doc/paper.tex
Using `P/pi` and `S/sigma` notation for EFTs.
Adding an example of **compensated** de Casteljau failing.
Updating comment about "bad" outcome for compensated de Casteljau.
Adding more to parenthetical phrase about u^4 term.

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/56877/32270
\usepackage{algorithm}
\usepackage{algpseudocode}

@@

  \begin{algorithmic}
    \Function{\(\left[x, y\right] = \mathtt{TwoSum}\)}{$a, b$}
      \State \(x = a \oplus b\)
      \State \(z = x \ominus a\)
      \State \(y = (a \ominus (x \ominus z)) \oplus (b \ominus z)\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

  \begin{algorithmic}
    \Function{\(\left[x, y\right] = \mathtt{Split}\)}{$a$}
      \State \(z = a \otimes (2^r + 1)\)
      \State \(x = z \ominus (z \ominus a)\)
      \State \(y = a \ominus x\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

  \begin{algorithmic}
    \Function{\(\left[x, y\right] = \mathtt{TwoProd}\)}{$a, b$}
      \State \(x = a \otimes b\)
      \State \(\left[a_h, a_l\right] = \mathtt{Split}(a)\)
      \State \(\left[b_h, b_l\right] = \mathtt{Split}(b)\)
      \State \(y = a_l \otimes b_l \ominus (((x \ominus a_h \otimes b_h)
          \ominus a_l \otimes b_h) \ominus a_h \otimes b_l)\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

  \begin{algorithmic}
    \Function{\(\left[x, y\right] = \mathtt{TwoProdFMA}\)}{$a, b$}
      \State \(x = a \otimes b\)
      \State \(y = \mathtt{FMA}(a, b, -x)\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

Consider de Casteljau's method to evaluate a degree \(n\)
polynomial in Bernstein-B\'{e}zier form with control points \(p_j\):
\begin{align*}
    b_j^{(0)} &= p_j \\
    b_j^{(k)} &= (1 - s) b_j^{(k - 1)} + s b_{j + 1}^{(k - 1)} \\
    b(s) &= b_0^{(n)}.
\end{align*}

@@

>>>>

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/56877/32270
\usepackage{algorithm}
\usepackage{algpseudocode}
%% H/T: https://tex.stackexchange.com/a/244805
\usepackage{booktabs,siunitx}

@@

  \begin{algorithmic}
    \Function{\(\left[S, \sigma\right] = \mathtt{TwoSum}\)}{$a, b$}
      \State \(S = a \oplus b\)
      \State \(z = S \ominus a\)
      \State \(\sigma = (a \ominus (S \ominus z)) \oplus (b \ominus z)\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

  \begin{algorithmic}
    \Function{\(\left[h, \ell\right] = \mathtt{Split}\)}{$a$}
      \State \(z = a \otimes (2^r + 1)\)
      \State \(h = z \ominus (z \ominus a)\)
      \State \(\ell = a \ominus h\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

  \begin{algorithmic}
    \Function{\(\left[P, \pi\right] = \mathtt{TwoProd}\)}{$a, b$}
      \State \(P = a \otimes b\)
      \State \(\left[a_h, a_{\ell}\right] = \mathtt{Split}(a)\)
      \State \(\left[b_h, b_{\ell}\right] = \mathtt{Split}(b)\)
      \State \(\pi = a_{\ell} \otimes b_{\ell} \ominus (((P \ominus
          a_h \otimes b_h)
          \ominus a_{\ell} \otimes b_h) \ominus a_h \otimes b_{\ell})\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

  \begin{algorithmic}
    \Function{\(\left[P, \pi\right] = \mathtt{TwoProdFMA}\)}{$a, b$}
      \State \(P = a \otimes b\)
      \State \(\pi = \mathtt{FMA}(a, b, -P)\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

Consider de Casteljau's method to evaluate a degree \(n\)
polynomial in Bernstein-B\'{e}zier form with control points \(p_j\):
\begin{align*}
    b_j^{(n)} &= p_j \\
    b_j^{(k)} &= (1 - s) b_j^{(k + 1)} + s b_{j + 1}^{(k + 1)} \\
    b(s) &= b_0^{(0)}.
\end{align*}

@@

\subsection{Example of Compensated de Casteljau Failing}

Consider
\[p(s) = (4s - 3)^3 (8s + 7) = (-189) b_{0, 4}(s) + (-54) b_{1, 4}(s) +
57 b_{2, 4}(s) + (-32) b_{3, 4}(s) + 15 b_{4, 4}(s)\]
at the point \(s = \frac{3}{4} + 800 u\). In exact arithmetic, we
have \(p(s) = 2^{38.6} u^3 + \mathcal{O}\left(u^4\right)\).
However, using the compensated de Casteljau algorithm results in
\(\widehat{p} + \widehat{e} = 0\):

\begin{center}
  \begin{tabular}{>{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$}}
    \toprule
    k & j & b_j^{(k)} & e_j^{(k)} \\
    \midrule
    3 & 0 & -87\frac{3}{4} + 108032u & -32u \\
    3 & 1 & 29\frac{1}{4} + 88768u & 32u \\
    3 & 2 & -9\frac{3}{4} - 71200u & 0 \\
    3 & 3 & 3\frac{1}{4} + 37600u & 0 \\
    \midrule
    2 & 0 & 187200u & -15360000u^2 \\
    2 & 1 & -62408u & 8u - 128000000u^2 \\
    2 & 2 & 20800u & 87040000u^2 \\
    \midrule
    1 & 0 & -6u - 199688192u^2 & \boxed{6u - 99831808u^2} \\
    1 & 1 & -2u + 66568192u^2  & \boxed{2u + 33271808u^2} \\
    \midrule
    0 & 0 & -3u + 7296u^2 & \boxed{3u - 7296u^2} \\
    \bottomrule
  \end{tabular}
\end{center}
This is due to dropped terms: \(e_0^{(1)}\) drops \(-90112000000u^3\),
\(e_1^{(1)}\) drops \(172032000000u^3\), \(e_0^{(0)}\) drops
\(319488000000u^3\) (that's relative to the \textbf{incorrect} \(e_j^{(1)}\)
terms, if compared to the correct terms there'd also be a \(u^4\) term
dropped).
